Evidence for an Intrinsic Color Parameter in Type~Ia Supernovae

### 2016-09-04 forgerard.tex
plowing along

\title{text}
\author
{
    G.~Aldering,\altaffilmark{2}
    P.~Antilogus,\altaffilmark{4}
    S.~Bailey,\altaffilmark{2}
    C.~Baltay,\altaffilmark{5}
    K.~Barbary,\altaffilmark{3}
    D.~Baugh,\altaffilmark{6}
    K.~Boone,\altaffilmark{2,3}
    S.~Bongard,\altaffilmark{4}
    C.~Buton,\altaffilmark{7}
    J.~Chen,\altaffilmark{6}
    N.~Chotard,\altaffilmark{7}
    Y.~Copin,\altaffilmark{7}
    P.~Fagrelius,\altaffilmark{2,3}
    H.~K.~Fakhouri,\altaffilmark{2,3}
    U.~Feindt,\altaffilmark{9}
    D.~Fouchez,\altaffilmark{10}
    E.~Gangler,\altaffilmark{11}  
    B.~Hayden,\altaffilmark{2}
    W.~Hillebrandt,\altaffilmark{16}
    A.~G.~Kim,\altaffilmark{2}
    M.~Kowalski,\altaffilmark{9,12}
    P.-F.~Leget,\altaffilmark{11}
    S.~Lombardo,\altaffilmark{9}
    J.~Nordin,\altaffilmark{2,9}
    R.~Pain,\altaffilmark{4} 
    E.~Pecontal,\altaffilmark{13}
    R.~Pereira,\altaffilmark{7}
    S.~Perlmutter,\altaffilmark{2,3}
    D.~Rabinowitz,\altaffilmark{5}
    M.~Rigault,\altaffilmark{9} 
    D.~Rubin,\altaffilmark{2,14}
    K.~Runge,\altaffilmark{2}
    C.~Saunders,\altaffilmark{2,3}
   R.~Scalzo,\altaffilmark{8}
    G.~Smadja,\altaffilmark{7} 
    C.~Sofiatti,\altaffilmark{2,3} 
    A.~Stocker,\altaffilmark{1}
    N.~Suzuki,\altaffilmark{2}
    S.~Taubenberger,\altaffilmark{16}
    C.~Tao,\altaffilmark{6,10}
    R.~C.~Thomas,\altaffilmark{15} \\
    (The Nearby Supernova Factory)
}

@@

\keywords{text}

\section{Introduction}
Type~Ia supernovae (SNe~Ia) form a homogenous set of astronomical objects and as such were recognized as a powerful distance indicator 
and probe of cosmology \citep{1992ARA&A..30..359B}.  After further careful consideration of supernova data, it was recognized
that SN~Ia light-curve shapes \citep{1984SvA....28..658P, 1993ApJ...413L.105P} and colors \citep{1998A&A...331..815T} exhibit subtle signs of heterogeneity,
which need to be considered when inferring SN~Ia distances.  Empirical models parameterizing SNe~Ia by their light-curve shape
and color were developed \citep{1996ApJ...473...88R, 1999ApJ...517..565P} to enable distance measurements of cosmological supernovae
that subsequently were used in the discovery of the accelerating expansion of the Universe \citep{1998AJ....116.1009R,1999ApJ...517..565P}.

The two most commonly used supernova light-curve fitters for cosmological purposes today are SALT2 \citep{2007A&A...466...11G} and MLCS2k2
\citep{2007ApJ...659..122J}.\footnote{More flexible light-curve fitters
\citep[e.g.][]{2011AJ....141...19B} are used to study SN~Ia heterogeneity.}
They remain two-parameter models, with one parameter characterizing light-curve shape and the other
supernova color.  SALT2 training extracts color variation empirically from SNe that span a wide range of colors whereas MLCS2k2
attributes color to the attenuation of light from host-galaxy dust. Neither model accommodates the naive expectation that
both intrinsic and extrinsic color variation may occur.

There is evidence that supports the expectation that one parameter in insufficient to describe the full range
of supernova color behavior.  One approach to look for color diversity is to find correlations between color and spectral features.
\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two populations with differing $B_{max}-V_{max}$ identified by Si velocity.
\citet{2015MNRAS.451.1973S}
find that high-velocity Si II$\lambda$6355 are found in objects that have red ultraviolet/optical colors near maximum brightness.
Another approach to probe color diversity is to use multiple colors of a single supernova to infer individual differential reddening. 
\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find on average values for $R_V \ll 3.1$,
much smaller than that of diffuse Milky Way dust, though the dispersion is large.
The also confirm the \citet{2011ApJ...729...55F} finding hat low $R_V$ is associated with high-extinction supernovae.
The above evidence has lead to the hypothesis that multiple scattering from circumstellar dust
plays a role in observed supernova colors \citep{2005ApJ...635L..33W, 2008ApJ...686L.103G}.
In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
the standard $R_V=3.1$ is recovered.

@@

If interpreted as being due to dust, the extrinsic term could be associated with extinction $A_X = \gamma_X k$.  In
this parlance our parameters can be re-expressed as the more familiar color excess
$E(B-V) = (\gamma_1-\gamma_2) k$ and total-to-selective extinction $R_X = \frac{\gamma_X}{\gamma_1-\gamma_2}$.
Similarly we introduce for the intrinsic color term $E_\delta(B-V) = (\delta_1-\delta_2) D$ and $R_{\delta X} = \frac{\delta_X}{\delta_1-\delta_2}$.

@@

The distribution of color excess $E(B-V) =(\gamma_1-\gamma_2)k$ and
 $E_\delta(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
Recall that given our boundary conditions the means of both distributions are equal to zero. 
The standard deviation of $E(B-V)$ is 0.078 mag while that of $E_\delta(B-V)$ is 0.019 mag.
The range of $B-V$ colors is $\sim 4$ times larger for the external contribution:
extreme colors can thus be attributed to the external source. 
Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/ebv.pdf}
   \caption{Histograms of the contributions to color excess from external $E(B-V) =(\gamma_1-\gamma_2)k$ and
   internal $E_\delta(B-V) = (\delta_1-\delta_2)D$ effects for the supernovae in our sample.
   \label{ebv:fig}}
\end{figure}

The two separate color effects are conflated into a combined color excess with a single effective total-to-selective extinction
\begin{equation}
R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)D}.
\label{RVeff:eqn}
\end{equation}
The distribution for $R_{V,eff}$ for the supernovae in our sample is shown in Figure~\ref{rveff:fig}
and has mean and standard deviation  $R_{V,eff}  = 1.52 \pm 0.24$.  
Rerunning the posterior calculation with initial conditions for $\gamma$  that correspond to $R_{X,eff}$ 
and $\delta=0$ (technically $\delta_0 = -\epsilon$ due to the $\delta_0<0$ condition)
reproduces the original results, indicating that
the effective and true $R$ values are not separated by local posterior extrema.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/rveff.pdf}
   \caption{The effective dust law of the two color terms combined $R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)D}$,
   for the supernovae in our sample.
   \label{rveff:fig}}
\end{figure}

@@

Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
$\Delta$: their distributions for all Monte Carlo chain links for all supernovae, are shown in Figure~\ref{perobject:fig}.
There is a core concentration in the  parameter-space, with around ten objects occupy its outskirts.
Many outliers appear in the red tail of $E(B-V)$, as would be expected in the infrequent selection of supernovae
heavily extinguished by host-galaxy dust; note that $E_\delta(B-V)$ does not have an analogous tail.
Outliers in  $EW_{Ca}$--$v_{Si}$ parameters are also clearly distinguished.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/perobject_corner.pdf} 
   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
$\Delta$.
   \label{perobject:fig}}
\end{figure}

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$ are given in the matrix
\begin{equation}
\begin{pmatrix}
1.000 & -0.012 & -0.031 & -0.026 & 0.070 & 0.002 \\
-0.012 & 1.000 & 0.128 & -0.331 & -0.064 & -0.004 \\
-0.031 & 0.128 & 1.000 & -0.182 & -0.155 & -0.024 \\
-0.026 & -0.331 & -0.182 & 1.000 & 0.018 & 0.036 \\
0.070 & -0.064 & -0.155 & 0.018 & 1.000 & 0.062 \\
0.002 & -0.004 & -0.024 & 0.036 & 0.062 & 1.000
\end{pmatrix}.
\end{equation}
Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  The second strongest is in
$EW_{Si}$--$v_{Si}$.
External $E(B-V)$ dust most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation stronger with internal parameters stronger than
0.04.  Although $E(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062.

@@

In our model, the observed color excess is attributed to contributions from extrinsic
$E(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ origins.
Among the supernovae in the SNfactory training set, the highest median value for 
$E(B-V)$ is $  0.33^{  +0.04}_{ -0.04}$ and for $E_\delta(B-V)$ is
$  0.07^{  +0.03}_{ -0.03}$ 
(see Figure~\ref{ebv:fig}).
In both parameters SN~2014J lives well outside the range of supernovae used to train the coefficients of the model.

@@

\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F_V<3$ encountered by the SN~Ia population.
Our model can explain a wide range of effective total-to-selective extinction with a single fixed set of $\gamma$ parameters, consistent
with $R^F_V=2.5$.  The reality is that a range of dust behaviors is expected; while this cannot accommodated in our model, it could be by
introducing hierarchical 
modeling of the $\gamma$ distribution.
For the moment, we assert that variations in extrinsic dust are limited in
size by Eqn.~\ref{color_sd:eqn} and positive correlations possible within \ref{color_cor:eqn}.

\citet{2011ApJ...729...55F, 2014ApJ...789...32B, 2015MNRAS.453.3300A} find that supernovae with large $E^o(B-V)$ 
preferentially exhibit low $R^F_V$.  This is natural in our model, as for a fixed extrinsic dust, $R_{V,eff}$ decreases with increasing $E^o(B-V)$ when
both are positive.

\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, whereas
our values of $\eta$ are consistent with zero.  Recall that we find a correlation between $v_{Si}$ and $EW_{Ca}$;
removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We  predict that a reanalysis of the previous data using equivalent width in place
of SiII velocity would also show correlations with color.

Anti-connection between $EW(Ca)$ and $v_{Si}$.  Intermediate mass

@@

The model and results presented here
carry information on the calibration of absolute magnitude.  The grey parameter $\Delta$ represent Hubble residuals after
application of the model, and its  $0.096$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
measurement uncertainties.  It is also subject to overtraining.
The  analysis of this article was intended to model the color behavior of supernovae in our dataset,
and is not appropriate for inferring the intrinsic dispersion.  A separate analysis is required to determine how
well this model can be used to measure supernova distances.

Low correlation coefficient means that the contribution of $E_\delta$ is not systematic, no high $E(B-V)$ bias.

Could affect distance determinations.  Large $E(B-V)$ does not mean extinction.

Standard candle.
\acknowledgments

>>>>

\title{Evidence for an Intrinsic Color Parameter in Type~Ia Supernovae}
\author
{
    A.~G.~Kim,\altaffilmark{2}
    G.~Smadja,\altaffilmark{7} 
    G.~Aldering,\altaffilmark{2}
    P.~Antilogus,\altaffilmark{4}
    S.~Bailey,\altaffilmark{2}
    C.~Baltay,\altaffilmark{5}
    K.~Barbary,\altaffilmark{3}
    D.~Baugh,\altaffilmark{6}
    K.~Boone,\altaffilmark{2,3}
    S.~Bongard,\altaffilmark{4}
    C.~Buton,\altaffilmark{7}
    J.~Chen,\altaffilmark{6}
    N.~Chotard,\altaffilmark{7}
    Y.~Copin,\altaffilmark{7}
    P.~Fagrelius,\altaffilmark{2,3}
    H.~K.~Fakhouri,\altaffilmark{2,3}
    U.~Feindt,\altaffilmark{9}
    D.~Fouchez,\altaffilmark{10}
    E.~Gangler,\altaffilmark{11}  
    B.~Hayden,\altaffilmark{2}
    W.~Hillebrandt,\altaffilmark{16}
    M.~Kowalski,\altaffilmark{9,12}
    P.-F.~Leget,\altaffilmark{11}
    S.~Lombardo,\altaffilmark{9}
    J.~Nordin,\altaffilmark{2,9}
    R.~Pain,\altaffilmark{4} 
    E.~Pecontal,\altaffilmark{13}
    R.~Pereira,\altaffilmark{7}
    S.~Perlmutter,\altaffilmark{2,3}
    D.~Rabinowitz,\altaffilmark{5}
    M.~Rigault,\altaffilmark{9} 
    D.~Rubin,\altaffilmark{2,14}
    K.~Runge,\altaffilmark{2}
    C.~Saunders,\altaffilmark{2,3}
   R.~Scalzo,\altaffilmark{8}
    C.~Sofiatti,\altaffilmark{2,3} 
    N.~Suzuki,\altaffilmark{2}
    S.~Taubenberger,\altaffilmark{16}
    C.~Tao,\altaffilmark{6,10}
    R.~C.~Thomas,\altaffilmark{15} \\
    (The Nearby Supernova Factory)
}

@@

\keywords{supernovae: general}

\section{Introduction}
Type~Ia supernovae (SNe~Ia) form a homogenous set of exploding stars and as such were early recognized as a powerful distance indicator 
and probe of cosmology \citep{1992ARA&A..30..359B}.  After further careful consideration of supernova data, it was recognized
that SN~Ia light-curve shapes \citep{1984SvA....28..658P, 1993ApJ...413L.105P} and colors \citep{1998A&A...331..815T} exhibit subtle signs of heterogeneity,
which being correlated with absolute magnitude
need to be considered when inferring distances.  Empirical models parameterizing SNe~Ia by their light-curve shape
and color were developed \citep{1996ApJ...473...88R, 1999ApJ...517..565P} that enabled distance measurements of cosmological supernovae,
which 
were subsequently used in the discovery of the accelerating expansion of the Universe \citep{1998AJ....116.1009R,1999ApJ...517..565P}.

The two most commonly used supernova-cosmology light-curve fitters today are SALT2 \citep{2007A&A...466...11G} and MLCS2k2
\citep{2007ApJ...659..122J}.\footnote{More flexible light-curve fitters
\citep[e.g.][]{2008ApJ...681..482C, 2011AJ....141...19B} are used to study SN~Ia heterogeneity.}
They remain two-parameter models, with one parameter characterizing light-curve shape and the other
supernova color.  The physical cause of the color diversity is viewed differently by the two sets of authors: 
\citet{2007A&A...466...11G} pragmatically extract color variation empirically from SNe that span a wide range of colors, with no attribution of
that variation to intrinsic or extrinsic origins;
\citet{2007ApJ...659..122J}
attribute changes in color to the attenuation of light from host-galaxy dust. Neither model accommodates the naive expectation that
both intrinsic and extrinsic color variation can occur independently.

There is evidence that supports the expectation that a single parameter cannot describe the full range
of supernova color behavior.  One approach to look for color diversity is to find correlations between color and spectral features.
\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two populations distinguished
by Si velocity with differing $B_{max}-V_{max}$.
\citet{2015MNRAS.451.1973S}
find that high-velocity Si II$\lambda$6355 are found in objects that have red ultraviolet/optical colors near maximum brightness.
Another approach to probe color diversity is to use multiple colors of a single supernova to infer individual differential reddening. 
\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find a wide
range of total-to-selective extinction with average values significantly lower than $R_V = 3.1$,
the canonical value for diffuse Milky Way dust.
The also confirm the \citet{2011ApJ...729...55F} finding that low $R_V$ is associated with high-extinction supernovae.
The above evidence has lead to the hypothesis that multiple scattering from circumstellar dust
plays a role in observed supernova colors \citep{2005ApJ...635L..33W, 2008ApJ...686L.103G}.
In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
the standard $R_V=3.1$ is recovered.

@@

If interpreted as being due to dust, the extrinsic term could be associated with extinction $A_X = \gamma_X k$.  In
this parlance our parameters can be re-expressed as the more familiar color excess
$E_\gamma(B-V) = (\gamma_1-\gamma_2) k$ and total-to-selective extinction $R_X = \frac{\gamma_X}{\gamma_1-\gamma_2}$.
Similarly we introduce for the intrinsic color term $E_\delta(B-V) = (\delta_1-\delta_2) D$ and $R_{\delta X} = \frac{\delta_X}{\delta_1-\delta_2}$.

@@

The distribution of color excess $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
 $E_\delta(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
Recall that given our boundary conditions the means of both distributions are equal to zero. 
The standard deviation of $E(B-V)$ is 0.078 mag while that of $E_\delta(B-V)$ is 0.019 mag.
The range of $B-V$ colors is $\sim 4$ times larger for the external contribution:
extreme colors can thus be attributed to the external source. 
Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/ebv.pdf}
   \caption{Histograms of the contributions to color excess from external $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
   internal $E_\delta(B-V) = (\delta_1-\delta_2)D$ effects for the supernovae in our sample.
   \label{ebv:fig}}
\end{figure}

For each supernova, the two separate color effects are conflated into an effective color excess
$E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and $B$-band ``extinction''
$A_{B, eff} = \gamma_1 k + \delta_1D$.  These values for the SNf sample
shown in Figure~\ref{rveff:fig}, overplotted with the expected relationship for color-excess 
purely due to the extrinsic $\gamma$ term.
Recall that  $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ respectively were arbitrarily assigned to the average $k$ and $D$ values of our distribution;
for convenience, we shift the zero of  $E_{eff}(B-V)$ so that the extrinsic dust expectation qualitatively forms a ridge line
bounding the high-extinction side of the distribution.
In the right plot of Figure~\ref{rveff:fig}, we show the difference between $E_{eff}(B-V)$ and that ridge line.
Over all effective color excesses, the inferred $R_B$  is capped by the canonical extrinsic value.
However, with increasing effective color excess there is a broadening of the distribution toward low inferred $R_B$,
accompanied by a decrease in average  $R_B$.
Supernovae with extremely red $E_{eff}(B-V)$ on average have significantly lower inferred $R_V$ that their counterparts with bluer $E_{eff}(B-V)$.
Conversely, supernovae with extreme
blue  $E_{eff}(B-V)$ fall slightly but noticeably above the ridge line, which would lead to an inferred $R_B$ slightly
larger than the extrinsic expectation.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/rveff.pdf}
   \includegraphics[width=2.8in]{output11/rveffres.pdf}
   \caption{Left: $E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and $B$-band``extinction''
$A_{B, eff} = \gamma_1 k + \delta_1D$ for the SNf sample.  Overplotted is the expected relationship for color-excess
purely due to the intrinsic $\gamma$ term.  we shift the zero of  $E_{eff}(B-V)$  so that the  the extrinsic dust expectation qualitatively forms a ridge line
bounding the high-extinction side of the distribution.
Right: The difference between $E_{eff}(B-V)$ and that ridge line.
   \label{rveff:fig}}
\end{figure}

@@

Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
$\Delta$: their distributions for all Monte Carlo chain links for all supernovae, are shown in Figure~\ref{perobject:fig}.
There is a core concentration in the  parameter-space, with around ten objects occupy its outskirts.
Many outliers appear in the red tail of $E_\gamma(B-V)$, as would be expected in the infrequent selection of supernovae
heavily extinguished by host-galaxy dust; note that $E_\delta(B-V)$ does not have an analogous tail.
Outliers in  $EW_{Ca}$--$v_{Si}$ parameters are also clearly distinguished.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/perobject_corner.pdf} 
   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
$\Delta$.
   \label{perobject:fig}}
\end{figure}

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$ are given in the matrix
\begin{equation}
\begin{pmatrix}
1.000 & -0.012 & -0.031 & -0.026 & 0.070 & 0.002 \\
-0.012 & 1.000 & 0.128 & -0.331 & -0.064 & -0.004 \\
-0.031 & 0.128 & 1.000 & -0.182 & -0.155 & -0.024 \\
-0.026 & -0.331 & -0.182 & 1.000 & 0.018 & 0.036 \\
0.070 & -0.064 & -0.155 & 0.018 & 1.000 & 0.062 \\
0.002 & -0.004 & -0.024 & 0.036 & 0.062 & 1.000
\end{pmatrix}.
\end{equation}
Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  The second strongest is in
$EW_{Si}$--$v_{Si}$.
External $E_\gamma(B-V)$ dust most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation stronger with internal parameters stronger than
0.04.  Although $E_\gamma(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062.

@@

In our model, the observed color excess is attributed to contributions from extrinsic
$E_\gamma(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ origins.
Among the supernovae in the SNfactory training set, the highest median value for 
$E_\gamma(B-V)$ is $  0.33^{  +0.04}_{ -0.04}$ and for $E_\delta(B-V)$ is
$  0.07^{  +0.03}_{ -0.03}$ 
(see Figure~\ref{ebv:fig}).
In both parameters SN~2014J lives well outside the range of supernovae used to train the coefficients of the model.

@@

\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F_V<3$ encountered by the SN~Ia population.
\citet{2011ApJ...729...55F} and the above authors
find that supernovae with large $E^o(B-V)$ 
preferentially exhibit low $R^F_V$. 
Our model predicts both of these effects with a single set of extrinsic dust parameters, as is borne out by the
SNf sample as shown in Figure~\ref{rveff:fig}. 
Our model also predicts that the converse also holds: supernovae with the smallest $E^o(B-V)$ due to intrinsic color
will appear overly faint when analyzed within the context of a canonical dust.
The trend in Figure~\ref{rveff:fig} showing an increased range of brighter-than-expected magnitudes  with increasing $E_{eff}(B-V)$  can
be compared
to Figure~\ref{betoule:fig}, which shows the $B$-band  Hubble residuals as a function of color from \citet{2014A&A...568A..22B}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/betoule.pdf} 
   \caption{Best-fit SN~Ia  $B$-band Hubble residuals as a function of the best-fit color parameter $C$ from the cosmology analysis of \citet{2014A&A...568A..22B}.
   \label{betoule:fig}}
\end{figure}

\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, whereas
our values of $\eta$ are consistent with zero.  Recall that we find a correlation between $v_{Si}$ and $EW_{Ca}$;
removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We  anticipate that for the in the previous analysis, equivalent widths of $CaII$ and
$SiII$ would also have shown correlations with color.

@@

The model and results presented here
carry information on the calibration of absolute magnitude.  The grey parameter $\Delta$ represent Hubble residuals after
application of the model, and its  $0.096$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
measurement uncertainties.  It is also subject to overtraining.
The  analysis of this article was intended to model the color behavior of supernovae in our dataset.
A separate analysis is required to determine how
well this model can be used to measure supernova distances.
We wait for this analysis to explore correlations between Hubble residuals, host-galaxy parameters (e.g.\ mass,
local star formation rate) and the intrinsic $D$ parameter.

The model introduced in this article is limited, in that it doesn't accommodate the expected diversity
in extrinsic dust properties that supernovae in different hosts may encounter.  Extending our model to 
include  a parameterized  $\gamma$ distribution would consider a range of host-dust behavior, and
is a direction of further study.
For the moment, we assert that variations in extrinsic dust are limited in
size by Eqn.~\ref{color_sd:eqn} and positive correlations possible within Eqn.~\ref{color_cor:eqn}.

\acknowledgments
